|

### 2023-04-08 paper.Rmd
Use discrete instead of discrete uniform across the paper

```{r results='asis'}
data.frame(j = c("2", "3", "6", "18", ""),
           sigma = c("0.25", "1.00", "2.00", "4.00", ""),
           a = c("-1", "0", "1", "", ""),
           b = c("0.25", "1.00", "4.00", "16.00", "64.00"),
           n = c("50", "100", "300", "", ""), 
           x_dist = c("Uniform", "Normal", "Skewed", "Discrete uniform", "")) %>%
  knitr::kable(col.names = NULL,
               align = "rr|rr|rc",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Levels of the factors used in data collection periods I, II, III.', 
               label = "model-factor-table" ) %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  kableExtra::add_header_above(c("Poly Order (sym1)", #"Order of Hermite polynomial\n(sym1)", 
                                 "SD (sym3)", #"Standard deviation of polynomial model\n(sym3)",
                                 "Shape (sym4)", # "Shape of heteroskedasticity\n(sym4)", 
                                 "Ratio (sym5)", # Variance factor of heteroskedasticity model\n(sym5)",
                                 "Size (sym6)", 
                                 "Distribution of fitted values")) %>% #"Sample size\n(sym6)")) %>%
  kableExtra::add_header_above(c("Non-linearity" = 2, 
                               "Heteroskedasticity" = 2, "Common" = 2)) %>%
  as.character() %>%
  gsub("sym1", "$j$", .) %>%
  gsub("sym3", "$\\\\sigma$", .) %>%
  gsub("sym4", "$a$", .) %>%
  gsub("sym5", "$b$", .) %>%
  gsub("sym6", "$n$", .) %>%
  cat()
```

@@

Fitted values are a function of the independent variables, and the distribution of the observed values affects the distribution of the fitted values. In the best case scenario the fitted values will have a uniform distribution, which means that there is even coverage of possible observed values across all of the predictors. This is not always present in the collected data. Sometimes the fitted values are discrete because one or more predictors were measured discretely. The distribution may be relatively Gaussian, reflecting a linear combinatio of many predictors, adhering to the Central Limit Theorem. It is also common to see a skewed distribution of fitted values, if one or more of the predictors has a skewed distribution. This latter problem is usually corrected before modelling using a variable transformation. Our simulation assess this by using four different distributions to represent fitted values: (1) uniform, (2) normal, (3) skewed and (4) discrete uniform. This is constructed by defining the raw predictor $X_{raw}$ in four corresponding distributions: 
(1) $U(-1, 1)$, (2) $N(0, 0.3^2)$, (3) $lognormal(0, 0.6^2)/3$ and (4) $u\{1, 5\}$. We would expect that the best reading of residual plots occurs when the fitted values are uniformly distributed.

Three different sample sizes are used, $n=50, 100, 300$ across the experiments. We would expect considerable variation in the signal strength in the simulated data plots with smaller $n$. A sample size of 300 is typically enough for structure to be visible in a scatter plot reliably.

@@

dat_dist_4 <- poly_model(shape = 1,
                         x = {
                           raw_x <- rand_uniform_d(k = 5, even = TRUE); 
                           closed_form(~stand_dist(raw_x))
                           }, 
                         sigma = 0.5)$
  gen(300, computed = select(dat_dist_1, e)) %>%
  mutate(x_dist = "Discrete uniform")

# Generate and plot data for discrete uniform distribution
bind_rows(dat_dist_1, dat_dist_2, dat_dist_3, dat_dist_4) %>%
  mutate(x_dist = factor(x_dist, 
                         levels = c("Uniform", 
                                    "Normal", 
                                    "Skewed", 
                                    "Discrete uniform"))) %>%
  VI_MODEL$plot(remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light()) +
  xlab("Fitted values") +
  ylab("Residuals") +
  facet_wrap(~x_dist, ncol = 4, scales = "free")
```

@@

diff_x_dist_power_pred %>%
  mutate(x_dist = ifelse(x_dist == "even_discrete", 
                         "Discrete uniform", 
                         stringr::str_to_title(x_dist))) %>%
  mutate(type = factor(stringr::str_to_title(type), 
                       levels = c("Non-Linearity", 
                                  "Heteroskedasticity"))) %>%
  mutate(x_dist = factor(x_dist, 
                         levels = c("Uniform", 
                                    "Normal", 
                                    "Lognormal", 
                                    "Discrete uniform"))) %>%

>>>>

```{r results='asis'}
data.frame(j = c("2", "3", "6", "18", ""),
           sigma = c("0.25", "1.00", "2.00", "4.00", ""),
           a = c("-1", "0", "1", "", ""),
           b = c("0.25", "1.00", "4.00", "16.00", "64.00"),
           n = c("50", "100", "300", "", ""), 
           x_dist = c("Uniform", "Normal", "Skewed", "Discrete", "")) %>%
  knitr::kable(col.names = NULL,
               align = "rr|rr|rc",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Levels of the factors used in data collection periods I, II, III.', 
               label = "model-factor-table" ) %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  kableExtra::add_header_above(c("Poly Order (sym1)", #"Order of Hermite polynomial\n(sym1)", 
                                 "SD (sym3)", #"Standard deviation of polynomial model\n(sym3)",
                                 "Shape (sym4)", # "Shape of heteroskedasticity\n(sym4)", 
                                 "Ratio (sym5)", # Variance factor of heteroskedasticity model\n(sym5)",
                                 "Size (sym6)", 
                                 "Distribution of fitted values")) %>% #"Sample size\n(sym6)")) %>%
  kableExtra::add_header_above(c("Non-linearity" = 2, 
                               "Heteroskedasticity" = 2, "Common" = 2)) %>%
  as.character() %>%
  gsub("sym1", "$j$", .) %>%
  gsub("sym3", "$\\\\sigma$", .) %>%
  gsub("sym4", "$a$", .) %>%
  gsub("sym5", "$b$", .) %>%
  gsub("sym6", "$n$", .) %>%
  cat()
```

@@

Fitted values are a function of the independent variables, and the distribution of the observed values affects the distribution of the fitted values. In the best case scenario the fitted values will have a uniform distribution, which means that there is even coverage of possible observed values across all of the predictors. This is not always present in the collected data. Sometimes the fitted values are discrete because one or more predictors were measured discretely. The distribution may be relatively Gaussian, reflecting a linear combinatio of many predictors, adhering to the Central Limit Theorem. It is also common to see a skewed distribution of fitted values, if one or more of the predictors has a skewed distribution. This latter problem is usually corrected before modelling using a variable transformation. Our simulation assess this by using four different distributions to represent fitted values: (1) uniform, (2) normal, (3) skewed and (4) discrete. This is constructed by defining the raw predictor $X_{raw}$ in four corresponding distributions: 
(1) $U(-1, 1)$, (2) $N(0, 0.3^2)$, (3) $lognormal(0, 0.6^2)/3$ and (4) $u\{1, 5\}$. We would expect that the best reading of residual plots occurs when the fitted values are uniformly distributed.

Three different sample sizes are used, $n = 50, 100, 300$ across the experiments. We would expect considerable variation in the signal strength in the simulated data plots with smaller $n$. A sample size of 300 is typically enough for structure to be visible in a scatter plot reliably.

@@

dat_dist_4 <- poly_model(shape = 1,
                         x = {
                           raw_x <- rand_uniform_d(k = 5, even = TRUE); 
                           closed_form(~stand_dist(raw_x))
                           }, 
                         sigma = 0.5)$
  gen(300, computed = select(dat_dist_1, e)) %>%
  mutate(x_dist = "Discrete")

# Generate and plot data for discrete uniform distribution
bind_rows(dat_dist_1, dat_dist_2, dat_dist_3, dat_dist_4) %>%
  mutate(x_dist = factor(x_dist, 
                         levels = c("Uniform", 
                                    "Normal", 
                                    "Skewed", 
                                    "Discrete"))) %>%
  VI_MODEL$plot(remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light()) +
  xlab("Fitted values") +
  ylab("Residuals") +
  facet_wrap(~x_dist, ncol = 4, scales = "free")
```

@@

diff_x_dist_power_pred %>%
  mutate(x_dist = ifelse(x_dist == "even_discrete", 
                         "Discrete", 
                         stringr::str_to_title(x_dist))) %>%
  mutate(type = factor(stringr::str_to_title(type), 
                       levels = c("Non-Linearity", 
                                  "Heteroskedasticity"))) %>%
  mutate(x_dist = factor(x_dist, 
                         levels = c("Uniform", 
                                    "Normal", 
                                    "Lognormal", 
                                    "Discrete"))) %>%
